\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix
updating Section IV

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\bm{x}_{k}^{i}\equiv\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\bm{x}_{k}^{i}$, the $i$th state sample at the $k$th time step.

@@

\begin{figure}
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed algorithmic setup for propagating the joint state PDF as probability weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The location of the points $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ can be updated by Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ can be updated via discrete version of the proximal recursion (\ref{ProxRecursionInfiniteDim}).}}
\label{fig:BlockDiagm}
\end{figure}

>>>>

\begin{figure}[htpb]
\centering
\includegraphics[width=.8\linewidth]{BlockDiagm.pdf}
\caption{\small{Schematic of the proposed algorithmic setup for propagating the joint state PDF as probability weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$. The location of the points $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ can be updated by Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}); the corresponding probability weights $\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ can be updated via discrete version of the proximal recursion (\ref{ProxRecursionInfiniteDim}).}}
\label{fig:BlockDiagm}
\end{figure}

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\bm{x}_{k}^{i}\equiv\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\bm{x}_{k}^{i}$, the $i$th state sample at the $k$th time step. The schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta},\bm{\omega}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi},\bm{\eta}\right) \nonumber\\
&= \left(\prod_{i=1}^{n}m_{i}/\sigma_{i}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}\right).
\label{BringBackOriginalStateSpace}	
\end{align}
The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}.

@@
